Estimating duration in the presence of misclassification

### 2024-03-20 ATACCC.tex
improve ATACCC plot

The modified model produced good fits to the data (see \cref{ATACCC:fig:goodness-of-fits}).
Almost all test results are captured in the 95\% credible intervals.
Individual 55 has some fitting issues, explored further below.
\begin{figure}
  \thisfloatpagestyle{empty}
  \vspace{-3cm}
  \makebox[\textwidth][c]{\includegraphics[width=.9\paperwidth]{ATACCC/fits}}
  \captionsetup{width=0.8\paperwidth}
  \captionof{figure}[Posterior predictive viral load fits]{Posterior predictive observed viral loads (median and 95\% CrI, lines and ribbon) for each individual, overlaid with their observed test results (dots). Posterior estimates are conditional on the result not being a false negative. Negative RT-PCR tests are plotted at the limit of detection, \ie a log viral load of 0. Each plot is labelled with the individual's position in the dataset, an arbitrary value. \label{ATACCC:fig:goodness-of-fits}}
\end{figure}

>>>>

The modified model produced good fits to the data (see \cref{ATACCC:fig:goodness-of-fits}).
Almost all test results are captured in the 95\% credible intervals.
Individual 55 has some fitting issues, explored further below.
\begin{figure}
  \makebox[\textwidth][c]{\includegraphics[width=.9\paperwidth]{ATACCC/fits}}
  \caption[Posterior predictive viral load fits]{Posterior predictive observed viral loads (median and 95\% CrI, lines and ribbon) for selected individuals, overlaid with their observed test results (dots). Posterior estimates are conditional on the result not being a false negative. Negative RT-PCR tests are plotted at the limit of detection, \ie a log viral load of 0. Each plot is labelled with the individual's position in the dataset, an arbitrary value. \label{ATACCC:fig:goodness-of-fits}}
\end{figure}
